Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-02-26 TEBenchmarkPaper/article.tex
Minor changes

We limit our discussion to applications in mathematics, although there are
similar approaches being applied to the task of \emph{scientific} discovery.
Scientific knowledge relies on inductive reasoning and experimental testing,
which are not so important to a mathematical theory. However, these techniques
do play an important role in many of the tools we investigate: in particular,
inductive reasoning allows a system to conjecture statements which may be too
difficult for it to deductively prove; whilst experimental testing, e.g. by
checking universally-quantified statements against some specific values, allows
many falsehoods to be quickly discarded without requiring more elaborate
symbolic reasoning.

@@

There are three aspects to consider when we evaluate an MTE system:

@@

% TODO: Should "generality" be one? Or is that just an implicit "don't cheat"
% assumption?

@@

Each system is run, and their output compared to the ground truth. To score
100\% on precision and recall, an MTE system must output all of the conjectures
which appear in the ground truth, and nothing else:

@@

This particular analysis takes its ground truths from the standard library of
the Isabelle theorem prover, with one involving the natural numbers, and the
other involving the list functions from figure \ref{figure:list_theory}. The
library authors have gone to the effort of stating, proving and including these
theorems in every copy of their software, which is a good indication that they
are useful or important.

>>>>

We limit our discussion to applications in mathematics, although there are
similar approaches being applied to the task of \emph{scientific} discovery.
Scientific knowledge relies on inductive reasoning and experimental testing,
which (in principle) are not so important to a mathematical theory. However,
these techniques \emph{do} play an important role in many existing formation and
exploration tools: in particular, inductive reasoning allows a system to
conjecture statements which may be too difficult for it to deductively prove;
whilst experimental testing, e.g. by checking universally-quantified statements
against some specific values, is a simple way to quickly discard many obvious
falsehoods generated by powerful but imperfect algorithms (as opposed to, say,
limiting ourselves to verified theorem generators).

@@

There are three aspects to consider when we evaluate a conjecture generation
system:

@@

We also make the assumption that the system is intended to be \emph{general},
and hence isn't hard-coded or fine-tuned to only perform well in a narrow
domain. Examples where this does \emph{not} hold include the natural number
heuristics of AM (discussed above), as well as machine learning models trained
on some specific dataset.

@@

Each system is run on these definitions, and their outputs are compared to the
ground truth. To score 100\% on precision and recall, an MTE system must output
all of the conjectures which appear in the ground truth, and nothing else:

@@

This particular analysis takes its ground truths from the standard library of
the Isabelle theorem prover, with one involving the natural numbers, and the
other involving the list functions from figure \ref{figure:list_theory}. Since
the library authors have gone to the effort of stating, proving and including
these theorems in every copy of their software, this is a good indication that
they are useful or important.
